\renewcommand{\abstractname}{\textsf{\Large{Acknowledgements}}}

\begin{abstract}

Er zijn heel veel mensen die me hebben geholpen bij mijn afstudeerproject, daarom zou ik ze graag willen bedanken. Allereerst is Edgar aan de beurt. Bedankt dat je me wilde begeleiden het afgelopen jaar. Jouw experimentele kennis is haast onuitputtelijk. Het was ook fijn dat je vanuit je ervaring altijd realistische doelen stelde. Dan is er Servaas, het meesterbrein achter het KAT-1 project. Dank voor het vertrouwen om aan dit project mee te mogen werken.     
 
Then I would like to thank Deon for being an excellent lab partner the last year. Things became a lot more enjoyable and productive after you arrived, and I think you are doing an excellent job on your PhD so far. Dan is er ook Ivo. Het was heel fijn dat ik af en toe aan kon kloppen om te sparren en ik vond het heel gezellig als je weer eens naar Eindhoven kwam. Then I would like to thank another incredibly talented PhD student Alex for many small and big helpful suggestions during our shared meetings, thanks for that. I would like to thank the other people from the UvA group as well: Robert and Florian. Thanks for teaching us Eindhoven people about strontium. 

Furthermore I would like to thank Robert and Madhav for taking the time to explain theoretical quantum physics concepts to an experimenalist. Ook wil ik graag Eddy en Hein bedanken voor onmisbare technische assistentie. Furthermore other people in the lab helped me with small and less small things, so thanks to Rik, Luc, Tim, Yang, Sheng and Daniel. Lastly I would like to thank other members of the CQT group for all the coffee breaks, seminars and borrels. I will look back happily during my stay at CQT.
    
\end{abstract}

\newpage