\noindent We report on the progress towards a neutral-atom based quantum co-processor.
As a first step towards this goal, we constructed a new apparatus that produces a magneto-optical trap in an optically contacted glass cell. 
We load $\sim 10^5$ Rb atoms in the magneto-optical trap at a temperature of $T=(2.2\pm0.2) \cdot 10^2$ $\mu$K.
Subsequently, the atoms are loaded in an array of optical tweezers made by a 820 nm far off-resonant titanium sapphire laser, a spatial light modulator and a glass-compensated ultra-long working distance microscope objective.
We measured the light distributions \textit{ex-situ} directly using a 0.85 NA objective, finding a near-diffraction limited waist of $0.79\pm0.05$ $\mu$m (theory: 0.75 $\mu$m) in the radial direction and a Rayleigh range of $6.2 \pm 0.5$ $\mu$m (diffraction theory: 3.0 $\mu$m) in the axial direction.
After aberration correction using the spatial-light modulator we find a corrected Rayleigh range $3.6\pm0.5$ $\mu$m.
The tweezer arrays showed a typical non-homogeneity of $\sim$ 7-12\%.
Larger arrays are typically less uniform than smaller ones. 
\textit{In-situ}, ultra-cold atoms loaded from the magneto-optical trap in the tweezer array are imaged into a sCMOS camera using the same objective used for the tweezers by splitting off the atomic fluorescence using a long pass dichroic mirror.
After averaging over multiple runs, we can detect fluorescence from atoms in tweezers for $2\times2$ and $2\times3$ arrays.
The amount of traps is limited by the available laser power. 
Upgrading to a camera that has lower noise should open up single-shot detection of atoms in these arrays. 
