\renewcommand{\abstractname}{\textsf{\Large{Acknowledgements}}}

\begin{abstract}

Er zijn heel veel mensen die me hebben geholpen bij mijn afstudeerproject, daarom zou ik ze graag willen bedanken. Allereerst Edgar: bedankt dat je me wilde begeleiden het afgelopen jaar. Jouw experimentele kennis is haast onuitputtelijk. Het was ook fijn dat je vanuit je ervaring altijd realistische doelen stelde. Dan is er Servaas, het meesterbrein achter het KAT-1 project. Dank voor het vertrouwen om aan dit project mee te mogen werken.     

Then I would like to thank Deon for last year. I really enjoyed spending time with you last year. I think a big part of the succeses we achieved are due to your ability to quickly adapt and improvise. Dan is er ook Ivo. Het was heel fijn dat ik af en toe aan kon kloppen om te sparren en ik vond het heel gezellig als je weer eens naar Eindhoven kwam. Then I would like to thank another incredibly talented PhD student Alex for many small and big helpful suggestions during our shared meetings, thanks for that. I would like to thank the other people from the UvA group as well: Robert and Florian. Thanks for teaching us Eindhoven people about strontium. Ook zou ik graag Rick van Bijnen willen bedanken omdat hij de tijd nam om vanuit Innsbrück even over SLM ideeën te sparren. 

Furthermore, I would like to thank Robert and Madhav for taking the time to explain theoretical quantum physics concepts to an experimentalist. Ook wil ik graag Eddy, Harry, Jeroen en Hein bedanken voor onmisbare technische assistentie. Moreover, other people in the lab helped me with small and less small things, so thanks to Rik, Luc, Tim, Yang, Sheng, and Daniel. Lastly, I would like to thank other members of the CQT group for all the coffee breaks, seminars, and borrels. I will look back happily during my stay at CQT.
    
\end{abstract}

\newpage